Price of Anarchy for Mean Field Games

### 2018-08-03 PoA.tex
updated Prop 1 and Corollary 1, moved Corollary 2

\begin{proposition}
Assuming (\ref{eq:assumptions}), if furthermore,
\begin{equation*}
\begin{split}
    \left[s\bar{q}(s-1)+\bar{b}_1\bar{\eta}_t^{MKV}\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    \bar{\eta}_t^{MKV}\bar{x}_t^{MKV}\left[(b^{MFG}-b^{MKV})b_2+(c^{MFG}-c^{MKV})\bar{b}_2\right]&=0,\ \forall t \in [0,T] \\
    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0,
\end{split}
\end{equation*}
then $PoA=1$.
\label{eq:lq_prop}
\end{proposition}

\begin{proof}
    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), the result is clear.
\end{proof}

\begin{corollary}
Assuming (\ref{eq:assumptions}), if furthermore, $\bar{b}_1=0$, $s\bar{q}(s-1)=0$, and $s_T\bar{q}_T(s_T-1)=0$ and at least one of the following holds: $b_2=\bar{b}_2=0$ or $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$
then $PoA=1$.
\label{corollary_1}
\end{corollary}

@@

\begin{corollary}
    Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then $PoA=1$.
\end{corollary}
\begin{proof}
    By equation (\ref{eq:x_bar_MFG_explicit}), $\mathbb{E}(\xi)=0$ implies $\bar{x}^{MFG}_t=0,\ \forall t \in [0,T]$. Therefore by Proposition \ref{prop:diff_SC}, $\Delta SC=0$. From equation (\ref{eq:v_t}), which we recall is equivalent to equation (\ref{eq:v_t_MKV}), $v_t>0$ which implies $h_{var}>0$. Therefore by equation (\ref{eq:SC_MKV_2}), $SC^{MKV}>0$. We conclude from equation (\ref{eq:PoA_LQ}) that $PoA=1$.
\end{proof}

>>>>

\begin{proposition}
Assuming (\ref{eq:assumptions}), if furthermore,
\begin{equation*}
\begin{split}
    \left[s\bar{q}(s-1)+\bar{b}_1\bar{\eta}_t^{MKV}\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    (b^{MFG}-b^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0,
\end{split}
\end{equation*}
then $PoA=1$.
\label{eq:lq_prop}
\end{proposition}

\begin{proof}
    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $c^{MFG}-c^{MKV}=b^{MFG}-b^{MKV}$, the result is clear.
\end{proof}

\begin{corollary}
Assuming (\ref{eq:assumptions}), if furthermore, $s\bar{q}(s-1)=0$, $\bar{b}_1=0$, $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$, and $s_T\bar{q}_T(s_T-1)=0$,
then $PoA=1$.
\label{corollary_1}
\end{corollary}

\begin{corollary}
	Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then from equation (\ref{eq:x_bar_MKV_explicit}), $x^{MKV}_t =0$ for all $t\in[0,T]$, and thus, $PoA=1$.
\end{corollary}

@@
